\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-16 paper/figures.tex
minor edits

\newcommand{\FigTapBandwidth}{
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.75\linewidth,clip]{figures/decoy-tap-bandwidth.png}
    \caption{\textbf{Tap Bandwidth}\,---\, %
        We deployed our \scheme implementation in a realistic ISP testbed on a
        (full duplex) tap of a 10~Gbps router. As shown in a typical week, traffic
        ranges from 2-17~Gbps.
    }
    \label{fig:tap-bandwidth}
\end{figure*}
}

@@

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,%
        We used PF\_RING to receive packets from a 10~Gbps packet tap, which we load balance
        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
        packets destined to registered phantom host addresses to a local application. The application
        determines if the client is legitimate (using a seed shared during registration) and forwards
        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.}
    \label{fig:implementation}
\end{figure}
}

>>>>

\newcommand{\FigTapBandwidth}{
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.75\linewidth,clip]{figures/decoy-tap-bandwidth.png}
    \caption{\textbf{Tap Bandwidth}\,---\, %
        We deployed our \scheme implementation in a realistic ISP testbed on a
        tap of a 20~Gbps router. As shown in a typical week, traffic
        ranges from 2-17~Gbps.
    }
    \label{fig:tap-bandwidth}
\end{figure*}
}

@@

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,%
        We used PF\_RING to receive packets from a 20~Gbps packet tap, which we load balance
        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
        packets destined to registered phantom host addresses to a local application. The application
        determines if the client is legitimate (using a seed shared during registration) and forwards
        their traffic to a proxy. Otherwise, the application responds as an innocuous host, such as by
        forwarding pakcets to a mask site.}
    \label{fig:implementation}
\end{figure}
}

### 2019-05-16 paper/paper.tex
minor edits

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
as Decoy Routing, has made promising steps towards that goal.
These techniques operate in the network's core, at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}.  Clients access circumvention service by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.  Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction is widely deployed~\cite{robinson2013collateral}.

@@

Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
%TODO: don't need to hedge on IPv4 anymore..?
\scheme supports both IPv4 and IPv6,
though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented Conjure (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}).  In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of network prefixes that the client knows can be used
for phantom hosts (previously distributed publicly).
The client and server hash the seed to determine which specific
IP address from the set of prefixes will be used and registered as a phantom host.
It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected phantom hosts and block them if
they pick up.
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, which can
later be used to verify a client connecting to the phantom host address is the
original registering client.
We discuss the intricacies of phantom IP address selection in
Section~\ref{sec:addr-selection}.

@@

We evaluated the performance of a client from an India-based VPS,
Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
measured by iperf for TapDance, our \scheme implementation, and a direct
connection to our iperf server in the ISP's network.

TapDance must reconnect if the amount of data sent by the client
exceeds a short TCP window (typically on the order of 32~KBytes) or the
connection persists until a timeout (18-120 seconds). At each reconnect, the
TapDance client naively blocks until a new TLS connection to the decoy and
station has been established. Thus, when uploading files, TapDance has to create
a new TLS connection for every 32~KBytes of data it sends, limiting its average
upload bandwidth to less than 1~Mbps due to the high overhead. In contrast,
our \scheme implementation is
able to maintain the same connection during large uploads, and achieves
performance inline with the direct connection.

During download-only workloads, TapDance is able to better utilize the network,
but must still reconnect before the decoy times out. In our tests, we see
TapDance reconnect every 25 seconds, which can negatively impact the performance of
downloads or any real-time streaming applications. Again, our \scheme
implementation is able to maintain a single connection and provide the maximum
download rate without interruption.

>>>>

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
as Decoy Routing, has made promising steps towards that goal.
These techniques operate in the network's core, at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}.  Clients access circumvention services by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.  Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction is widely deployed~\cite{robinson2013collateral}.

@@

Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
%TODO: don't need to hedge on IPv4 anymore..? couldcut
\scheme supports both IPv4 and IPv6,
though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented Conjure (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

%download: dd - td: 5947790000 - 5219112999 = 14% faster down
% upload:  5088330000/3500000.0 = 1453x upload
% latency: td avg 297ms, dd avg 237ms = 20% lower latency

@@

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of network prefixes that the client knows can be used
for phantom hosts (previously distributed publicly).
The client and server hash the seed to determine which specific
IP address from the set of prefixes will be used and registered as a phantom host.
It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected phantom hosts and block them if
they can be used as proxies.
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, which can
later be used to verify a client connecting to the phantom host address is the
original registering client.
We discuss the intricacies of phantom IP address selection in
Section~\ref{sec:addr-selection}.

@@

We evaluated the performance of a client from an India-based VPS,
Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
measured by iperf for TapDance, our \scheme implementation (using the mask site application),
and a direct connection to our iperf server in the ISP's network.

TapDance must reconnect if the amount of data sent by the client
exceeds a short TCP window (typically on the order of 32~KBytes) or the
connection persists until a timeout (18-120 seconds). At each reconnect, the
TapDance client naively blocks until a new TLS connection to the decoy and
station has been established. Thus, when uploading files, TapDance has to create
a new TLS connection for every 32~KBytes of data it sends, limiting its average
upload bandwidth to around 0.1~Mbps due to the high overhead. In contrast,
our \scheme implementation is
able to maintain the same connection during large uploads, and achieves
performance inline with the direct connection, over 1400 times faster.

During download-only workloads, TapDance is able to better utilize the network,
but must still reconnect before the decoy times out. In our tests, we see
TapDance reconnect every 25 seconds, which can negatively impact the performance of
downloads or any real-time streaming applications. Again, our \scheme
implementation is able to maintain a single connection and provide the maximum
download rate without interruption, 14\% faster than TapDance.

### 2019-05-16 paper/related.tex
minor edits

Traditionally, proxies deployed for censorship are eventually identified and
blocked by the censor. Several proposals have been made to carefully control
the distribution of proxy addresses, using social connections and
reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this
information secret is challenging; additionally, censors often employ active
scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction
networking generally assumes that clients have no secret information, and
instead relies on the  collateral damage that would result from blocking all
the potential decoy destinations. \scheme furthers this goal by creating a
large number of destinations out of the dark space. A similar approach was
conceptualized in DEFIANCE~\cite{lincoln2012}, where censored Tor clients
connect to pools of addresses that are volunteered to run Tor bridge nodes.
Unlike \scheme, DEFIANCE requires network admins that own the IP blocks to
participate and operate proxies on their addresses, allowing censors to block
the IP ranges involved once discovered. In contrast, \scheme can be
deployed at transit ISPs, and censors face a large risk of collateral
over-blocking if they block the network blocks used.
Another similar approach was
taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large
set of dummy destinations. CensorSpoofer, however, could only send information
in one direction---to the client---and had to rely on a separate out-of-band
channel for client-to-proxy communication. As an alternative approach,
FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to
run Flash- or WebRTC-based proxies within their browser to allow censored users
to connect to the Tor network with the potential to greatly increase the
number. In practice, these proxies served a very small number of users, as
compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

>>>>

Traditionally, proxies deployed for censorship are eventually identified and
blocked by the censor. Several proposals have been made to carefully control
the distribution of proxy addresses, using social connections and
reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this
information secret is challenging; additionally, censors often employ active
scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction
networking generally assumes that clients have no secret information, and
instead relies on the  collateral damage that would result from blocking all
the potential decoy destinations. \scheme furthers this goal by creating a
large number of destinations out of the dark space. A similar approach was
conceptualized in DEFIANCE~\cite{lincoln2012}, where censored Tor clients
connect to pools of addresses that are volunteered to run Tor bridge nodes.
DEFIANCE also requires volunteer web servers to run specialized servers to
distribute information. Unlike \scheme, DEFIANCE was not designed to run at an
ISP, and invovles many moving parts that present single points of failure if
blocked by a censor. In contrast, \scheme has a relatively simple yet flexible
design, allowing it to easily respond to censors.
Another similar approach was
taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large
set of dummy destinations. CensorSpoofer, however, could only send information
in one direction---to the client---and had to rely on a separate out-of-band
channel for client-to-proxy communication. As an alternative approach,
FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to
run Flash- or WebRTC-based proxies within their browser to allow censored users
to connect to the Tor network with the potential to greatly increase the
number. In practice, these proxies served a very small number of users, as
compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}
